\ttitle

### 2016-02-16 Chapters/BodyComp.tex
Body comp - more changes
- Some page layout changes

\subsection{Body composition vs. BMI/sex}
The body composition differences between male and female patients with increasing body mass index is shown in Figure \ref{fig:bc_gender_bmi} on page \pageref{fig:bc_gender_bmi}. 
There were significant differences in the proportion of subcutaneous adipose tissue versus visceral adipose tissue between males and females. 
Men generally had less subcutaneous fat but more visceral fat and skeletal muscle areas. 
However, the proportion of skeletal muscle in both males and females decreased significantly with increasing body mass index.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/bc_gender_bmi_pie}
	\caption[Differences in body composition according to sex and body mass index.]
	{Differences in body composition according to sex and body mass index.
	\\Body composition differed significantly between men and women and with increasing body mass index (BMI). The proportion of skeletal muscle area decreased with increasing BMI in both sexes but there was a larger decrease in women than men. Visceral adipose tissue contributed more to weight in obese men than subcutaneous adipose tissue while the opposite was true in women.}
	\label{fig:bc_gender_bmi}
\end{figure}

@@

>>>>

\subsection{Body composition vs. BMI/sex}

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/bc_gender_bmi_pie}
	\caption[Differences in body composition according to sex and body mass index.]
	{Differences in body composition according to sex and body mass index.
		\\Body composition differed significantly between men and women and with increasing body mass index (BMI). The proportion of skeletal muscle area decreased with increasing BMI in both sexes but there was a larger decrease in women than men. Visceral adipose tissue contributed more to weight in obese men than subcutaneous adipose tissue while the opposite was true in women.}
	\label{fig:bc_gender_bmi}
\end{figure}

The body composition differences between male and female patients with increasing body mass index is shown in Figure \ref{fig:bc_gender_bmi} on page \pageref{fig:bc_gender_bmi}. 
There were significant differences in the proportion of subcutaneous adipose tissue versus visceral adipose tissue between males and females. 
Men generally had less subcutaneous fat but more visceral fat and skeletal muscle areas. 
However, the proportion of skeletal muscle in both males and females decreased significantly with increasing body mass index.

@@

%\clearpage
